---
title: "ASSIGNMENT NO.: 1"
author: "Barun Kumar (18125760015)"
date: "27 November 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
*************************************************************************************
1. Using R Programming create User Defined Functions for the below formulae:
-------------------------------------------------------------------------------------
r, n, t parameters are used in all functions have meaning as mentioned below :

# r    = annual rate of interest
# n    = Number of years
# t    = Number of periods in a year

_________________________________________________________________________________

A. Future value = Present value(1+r)^n
_________________________________________________________________________________

Solution :
```{r}
cal_future_value <- function(pv,r,n,t){
  reff = r/(t*100)
  neff = n*t
  print("Future Value : ")
  return(pv*((1+reff)^neff))
}
```

Example :

```{r}

cal_future_value(1000,10,10,12)

```
_________________________________________________________________________________

B. Future value of an annuity = Constant periodic flow(A) [(1+r)^n - 1)/r]
_________________________________________________________________________________
```{r}

cal_future_value_annuity <- function(A,r,n,t){
  reff = r/(t*100)
  neff = n*t
  print("Future Value of annuity : ")
  return(A*(((1+reff)^neff)-1)/reff)
}

```

Example :

```{r}

cal_future_value_annuity(1000,8,5,4)

```
_________________________________________________________________________________

C. Present value = Future value x 1/(1+r)^n
_________________________________________________________________________________
```{r}

cal_present_value <- function(FV,r,n,t){
  reff = r/(t*100)
  neff = -n*t
  print("Present Value : ")
  return(FV*((1+reff)^neff))
}

```

Example :

```{r}

cal_present_value(1000,10,5,4)

```

_________________________________________________________________________________

D. Present value of an annuity = Constant periodic flow(A) [1 - 1/ (1+r)^n] /r
_________________________________________________________________________________
```{r}

cal_present_value_annuity <- function(A,r,n,t){
  reff = r/(t*100)
  neff = -n*t
  print("Present Value of annuity : ")
  return(A*((1-((1+reff)^(neff)))/reff))
}

```

Example :

```{r}

cal_present_value_annuity(1000,8,5,12)

```
_________________________________________________________________________________

E. Present value of a perpetuity = Constant periodic flow(A) [1/r]
_________________________________________________________________________________
```{r}

cal_present_value_perpetuity <- function(A,r){
  print("Present Value of perpetuity : ")
  return(A/r)
}

```

Example :

```{r}

cal_present_value_perpetuity(15000,8)

```



