---
title: "Assignment No. 1"
author: "Barun Kumar (18125760015)"
date: "30 November 2018"
output: html_document
---
SINGLE FUNCTION FOR TIME VALUE OF MONEY CALCULATIONS

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Function Definition

```{r}
cal_value <- function(a,b,r,n,t,meth){
  
# Calculation for Future and Present Value  
  if(meth == "FVPV"){
    
    if(a == "cal"){
      reff = r/(t*100)
      neff = n*t
      print("Future Value : ")
      return(b*((1+reff)^neff))
    }
    else if(b == "cal"){
      reff = r/(t*100)
      neff = n*t
      print("Present Value : ")
      return(a/((1+reff)^neff))
    }
    else if(r == "cal"){
      neff = n*t
      print("Annual rate of interest : ")
      return(((a/b)^(1/neff)-1)*t*100)
    }
    else if(n == "cal"){
      reff = r/(t*100)
      print("Period Value (in years) : ")
      return((log(a/b)/log(1+reff))/t)
    }
  }
  
# Calculation for Future Value of an annuity
  if(meth == "FVA"){
    if(a == "cal"){
      reff = r/(t*100)
      neff = n*t 
      print("Future Value of annuity : ")
      return(b*(((1+reff)^neff)-1)/reff)
    }
    else if(b == "cal"){
      reff = r/(t*100)
      neff = n*t 
      print("Constant Periodic Flow : ")
      return(a*reff/(((1+reff)^neff)-1))
    }
    else if(n == "cal"){
      reff = r/(t*100)
      print("Period Value (in years) : ")
      return(((log(((a*reff)/b)+1))/(log(1+reff)))/t)
    }
  }
  # Calculation for Present Value of an annuity
    if(meth == "PVA"){
    if(a == "cal"){
      reff = r/(t*100)
      neff = n*t 
      print("Present Value of annuity : ")
      return(b*(1-((1+reff)^(-neff)))/reff)
    }
    else if(b == "cal"){
      reff = r/(t*100)
      neff = n*t 
      print("Constant Periodic Flow : ")
      return(a*reff/(1-((1+reff)^(-neff))))
    }
    else if(n == "cal"){
      reff = r/(t*100)
      print("Period Value (in years) : ")
      return(-((log(1-((a*reff)/b)))/(log(1+reff)))/t)
    }
  }
}
```

*************************************************************************

FUTURE VALUE AND PRESENT VALUE

*************************************************************************
 a    = Future value
 b    = Present value
 r    = annual rate of interest
 n    = Number of years
 t    = Number of periods in a year
 meth = "FVPV" (FUTURE VALUE AND PRESENT VALUE calculation method)

Put "cal" in any variable whose value needs to be found in below function 
call and execute to get the solution

-------------------------------------------------------------------------

```{r}

cal_value(7449.229,5000,"cal",5,12,"FVPV")

```
******************************************************************************
********************************************************************************
FUTURE VALUE OF AN ANNUITY

******************************8***********************************************
 a    : Future value of an annuity
 b    : Constant periodic flow(A)
 r    : annual rate of interest
 n    : Number of years
 t    : Number of periods in a year
 meth : "FVPV" (FUTURE VALUE AND PRESENT VALUE calculation method)

Put "cal" in any variable whose value needs to be found in below function 
call and execute to get the solution

> Calculating r is complex so this function will not work for r calculation

-----------------------------------------------------------------------------
```{r}

cal_value("cal",500,12,5,4,"FVA")

```

-----------------------------------------------------------------------------

********************************************************************************
PRESENT  VALUE OF AN ANNUITY
********************************************************************************
 a    : Present value of an annuity
 b    : Constant periodic flow(A)
 r    : annual rate of interest
 n    : Number of years
 t    : Number of periods in a year
 meth : "FVPV" (FUTURE VALUE AND PRESENT VALUE calculation method)


Put "cal" in any variable whose value needs to be found in below function 
call and execute to get the solution

> Calculating r is complex so this function will not work for r calculation

-----------------------------------------------------------------------------

```{r}

cal_value(8175.717,500,8,"cal",4,"PVA")

```

-----------------------------------------------------------------------------
